Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.

### 2018-08-24 Manuscript/Manuscript.Rmd
Working on methods

**Meta-analysis**
To perform the first step, I used data from a metanalysis that gathered peak brain coordinates of activity from studies of valuation (n = 27 studies) and DMN (n = 77). These are the surviving areas post-statistical thresholding from each study. I analyzed this data by mapping the peak cortical coordinates to an atlas of the human cortical surface (Glasser et al., 2016). This produced a list of standardized parcels that were reported on each study. The advantage of utilizing this atlas was threefold: first, it reduced the number of functional vertices from 60,000 (cortical surface vertices) to 360 (cortical parcels). Second, it standardizes the vertices from the first to the second stage of my study. Finally, it allowed me to project each area on a brain space without much clutter. Since each vertex is embedded with topographical information, and since functional topography is essential to my question, I mostly project my results onto brain space.

I thus generated two undirected, loop-less, weighted graphs in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies. Since different decision tasks use different sensory modalities, and since sensory areas get sometimes reported as unrelated peak coordinates in DMN studies, I bootstrapped the co- occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile. Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded. With these graphs set up, I computed the strength and betweenness centrality in order to capture each parcel’s centrality in the valuation and DMN literatures separately.

In order to select of regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, I first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution. Next, I took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus my main target for dissociation).

**Whole Brain Parcellated connectivity**
For the second step, in order to actually quantify the intrinsic connectivity of these ROIs in the brain, I used data from the Human Connectome Project. Specifically, I acquired resting-state fMRI activity from 3 subjects, all of whom have been preprocessed according to industry standards to allow for group-level comparisons (Tobyne et al., 2017). Each data set contained around 1 hour of signals represented as 4800 time points, and each subject contained 60,000 vertices. I parcellated each subject’s brain according to the atlas mentioned above, so that each parcel contained the mean time series from its vertices, and correlated the mean time series among all parcels (Pearson). This produced a weighted adjacency matrix for each subject, where each of the 360 parcels is a vertex, and edges the correlations among all of them. Next, I took the exponential of the correlations, Fisher transformed them (i.e. tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant (FDR < 0.05). Again, I quantified each parcel’s strength and betweenness, averaged them across subjects, and examined whether any of the ROIs showed uniquely high centralities. For this, I performed a permutation comparing the mean strength between the ROIs and the rest of the brain for each participant.

>>>>

**Meta-analysis**
We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each peak volumetric coordinate, 10mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer. The sphere sections that overlapped with the cortex were mapped to an atlas of the human cortical surface (Glasser et al., 2016). This produced a list of standardized parcels that were reported on each study.

With these lists, we computed the number of times every two parcels co-occurred across each literature. This allowed us to generate two weighted networks in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies. In order to threshold the parcels that are most likely to belong to each lliterature, we bootstrapped the co-occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile of this distribution. Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded. The connectivity strength of every pairwise parcels was then calculated as the sum of their co-occurrences. In order to select regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, we first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution. Next, we took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus our main target for dissociation).

**Whole Brain Parcellated connectivity**
In order to actually quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state data from the Human Connectome Project (n = 80). Beyond the standard minimally preprocessed pipeline from HCP (), the data went through a number of additional refinements that are explained in detail elsewhere (Tobyne et al., 2017). Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR). Each data set contained around 1 hour of signals represented as approximately 4800 time points, and each subject contained 60,000 vertices. I parcellated each subject’s brain according to the atlas mentioned above, so that each parcel contained the mean time series from its vertices, and correlated the mean time series among all parcels (Pearson). This produced a weighted adjacency matrix for each subject, where each of the 360 parcels is a vertex, and edges the correlations among all of them. Next, I took the exponential of the correlations, Fisher transformed them (i.e. tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant (FDR < 0.05). Again, I quantified each parcel’s strength and betweenness, averaged them across subjects, and examined whether any of the ROIs showed uniquely high centralities. For this, I performed a permutation comparing the mean strength between the ROIs and the rest of the brain for each participant.
